Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-02 WSSSPE3/report/WSSSPE3_review.tex
Fix typos and minor rewriting.
Add a TODO note.
Added line breaks. No content change.
Minor changes to abstract.

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). 
The report includes a description of the keynote presentation and a set of lightning
talks, and focuses on the discussions, future steps, and future organization for
a set of self-organized working groups.
For each group, the report also includes a point of contact and a landing
page that can be used by those who want to join that group's future activities.
The main challenge left by the workshop is to see if the groups will carry
out these activities that they have scheduled, and how the WSSSPE community
can encourage its members to do so.

@@

\maketitle
%\newpage

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynote}\label{sec:keynote}
%\note{Lead: S.-C. Choi.  See \href{http://tinyurl.com/qbbqgsj}{slides} \& \href{http://tinyurl.com/q45kfcn}{video}.}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). 
The report includes a description of the keynote presentation and a set of lightning
talks. It also focuses on the discussions, future steps, and future organization for
a set of self-organized working groups.
For each group, we include a point of contact and a landing
page that can be used by those who want to join that group's future activities.
The main challenge left by the workshop is to see if the groups will execute 
these activities that they have scheduled, and how the WSSSPE community
can encourage its members to follow suit.

@@

\maketitle
\newpage

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynote \label{sec:keynote}}
%\note{Lead: S.-C. Choi.  See \href{http://tinyurl.com/qbbqgsj}{slides} \& \href{http://tinyurl.com/q45kfcn}{video}.}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
